Improving the portuguese hyphenation rules

### 2024-07-05 article/dictionary.tex
fix #49

The procedure to create the second list of hyphenated words involved several steps:
\begin{enumerate*}[label=\arabic*)]
  \item select those hyphenations agreed by five dictionaries, that have no alternative hyphenation proposal (5 to 0 votes);
  \item from those with alternative proposals, exam whether they constituted apparent proparoxytones (these cases could arise from instances with 5 to 1 votes or 6 to 1 votes, as explained earlier), 
      \begin{enumerate*}[label=\alph*)]
	  \item if the word had a diacritic, select the paroxytone option (e.g. \emph{po-lí-cia} instead of \emph{po-lí-ci-a} and \emph{pe-rí-neo} instead of \emph{pe-rí-ne-o}),
	  \item if not, choose the proparoxytone option (e.g. \emph{au-to-ri-a} instead of \emph{au-to-ri-a} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
	      % [gq]u-[aeio]
      \end{enumerate*}
  \item if the word did not fall into the apparent proparoxytone category, select the hyphenation with five votes.
\end{enumerate*}
This procedure was implemented in the script \texttt{get51.sh}. 
Only a few hyphenations required manual correction, including the following that were added:
\emph{quar-tzo}, \emph{quar-tzi-to}, \emph{su-bli-nha}, \emph{a-pnei-a}, \emph{dis-pnei-a}, 
\emph{hi-per-al-ge-si-a}, and \emph{neer-lan-dês}.
The final list, containing \num{\NumberOfFiveAgrees} additional hyphenations, is stored in \texttt{hyphenations5.dic}, 
bringing the total number of hyphenations across both lists to \num{\NumberOfSixFiveAgrees}.

>>>>

The procedure to create the second list of hyphenated words involved several steps:
\begin{enumerate*}[label=\arabic*)]
  \item select those hyphenations agreed by five dictionaries, that have no alternative hyphenation proposal (5 to 0 votes);
  \item from those with alternative proposals, exam whether they constituted apparent proparoxytones (these cases could arise from instances with 5 to 1 votes or 6 to 1 votes, as explained earlier), 
      \begin{enumerate*}[label=\alph*)]
	  \item if the word had a diacritic, select the paroxytone option (e.g. \emph{po-lí-cia} instead of \emph{po-lí-ci-a} and \emph{pe-rí-neo} instead of \emph{pe-rí-ne-o}),
	  \item if not, choose the proparoxytone option (e.g. \emph{au-to-ri-a} instead of \emph{au-to-ria} and \emph{mar-ce-nei-ro} instead of \emph{mar-ce-neiro})\footnote{We just have to make sure we are not selecting those cases where there is a sequence of the form \texttt{[gq]u-[aeio]} (using regex notation), as in \emph{a-pa-zi-gu-ar} and \emph{en-xa-gu-ar}.}.
	      % [gq]u-[aeio]
      \end{enumerate*}
  \item if the word did not fall into the apparent proparoxytone category, select the hyphenation with five votes.
\end{enumerate*}
This procedure was implemented in the script \texttt{get51.sh}. 
Only a few hyphenations required manual correction, including the following that were added:
\emph{quar-tzo}, \emph{quar-tzi-to}, \emph{su-bli-nha}, \emph{a-pnei-a}, \emph{dis-pnei-a}, 
\emph{hi-per-al-ge-si-a}, and \emph{neer-lan-dês}.
The final list, containing \num{\NumberOfFiveAgrees} additional hyphenations, is stored in \texttt{hyphenations5.dic}, 
bringing the total number of hyphenations across both lists to \num{\NumberOfSixFiveAgrees}.
